---
title: "Script to download data of scPDSI raster for US"
author: "Antonio J. Perez-Luque (@ajpelu)"
date: "22 Aug 2014"
output: 
    html_document:
       theme: united
       highlight: pygments
    md_document:
       variant: markdown_github
---
In this script we create a loop to download raster data of scPDSI from [West Wide Drought Tracker](http://www.wrcc.dri.edu/wwdt/). 

```{r someMetadata, eval=FALSE}
#-------------------------------------------------------------------
### Script to download data of PDSI raster from 1896 to 2014 
# August, 2014
# NCEAS Group OSS2014 
# @ajpelu 
# v1.0 
```

```{r packages, eval=FALSE} 
#-------------------------------------------------------------------
# Load packages 
library(RCurl)
#-------------------------------------------------------------------
```

First we need to set the directory to download the data. 
```{r directory, eval=FALSE}
#-------------------------------------------------------------------
# Set the directory 
di <- '/Users/ajpeluLap/myrepos/Drought_CA/pdsi/stpdsi/data/raster/2000'
setwd(di)
#-------------------------------------------------------------------
```

You can download data of scPDSI of other variables. To change the variable you need the url where the raster data are stored, and put it into `url.aux` variable of the below loop. In our case, the scPDSI, are in this [directory](http://www.wrcc.dri.edu/monitor/WWDT/data/PRISM/scpdsi). If you want to download other years, change the parameter `for (y in 2000:2014)` and set the year range you want to download. 


```{r loop, eval=FALSE}
#-------------------------------------------------------------------
# run only a time!!!!! 
# Raster data about scPDSI 
# http://www.wrcc.dri.edu/wwdt/archive.php?folder=scpdsi
# Loop to download the raster data 

for (y in 2000:2014) { 
# Get the url
  url.aux <- paste('http://www.wrcc.dri.edu/monitor/WWDT/data/PRISM/scpdsi/scpdsi_',y,'_', sep='')
  for (m in 1:12){
  url <- paste(url.aux,m,'_PRISM.nc', sep='') 
  filenamedest <- strsplit(url, split='http://www.wrcc.dri.edu/monitor/WWDT/data/PRISM/scpdsi/')[[1]][2]
  dest <- paste(y,sprintf("%02d",m),'.nc', sep='')
  download.file(url,dest)
}}

```


Sources: 

- Raster maps from [West Wide Drought Tracker](http://www.wrcc.dri.edu/wwdt/) [accessed 25 July 2014]

